---
title: '**Introduction to R Markdown**'
author: "Gustavo Rojas-Matute"
date: "10/8/2019"
output: word_document
bibliography: bibtest.bib
institution: "American University"
abstract: " This tutorial provides students with basic tools needed to work with R Markdown."

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction 

R Markdown is very versatil tool for researchers since allows the combination of codes and narratives to produce high quality reports in different formats including: pdf, html, word, beamer presentations, etc.

The best way to read this tutorial is open the R Markdown file and click "Knit", then read the R Markdown file and the html document at the same time. 

## R Markdown Definition

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 

## Installation

Like other R packages, the installation of R Markdown is as usual:

install.packages("rmarkdown")


## Starting R Markdown in R Studio

Go to RStudio: File -> New File -> R Markdown

## Types of Content

* A YAML header surrounded by three dashes "---", where the author can specify: title, author, institution, date, abstract, and type of documment or output(word_document, html_document, pdf_document, etc). 

For example:
---s 
title: "R Markdown Tutorial"
output: html_document 
---s

In the header you can also specify the BibTex file link to bibliography, and then cite the reference as usual, for example: @xie2019. Be sure that "bookdown" package is installed. 

* R code chunks surrounded bynthree backticks like "```". The lenguage of the code is specified inside the curly brackets: "{R}"



## Embeding Codes

You can embed an R code chunk like this:

```{r cars}
summary(cars)
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

## Regressions
Regression 1

```{r, echo=FALSE}
reg1 = lm(pressure ~ temperature , data = pressure)
summary(reg1)
require(memisc)
```


## Other regression
Regression 2
```{r , echo=FALSE}
reg = lm(dist ~ speed , data = cars)
summary(reg)
plot(reg)
abline(reg)
```

## ggplot2

ggplot2 
```{r ggplot2-chart, echo=FALSE}
library(ggplot2)
ggplot(cars, aes(x=speed, y =dist)) + geom_point()+
  theme_bw()+
  labs(x = "speed", y = "Dist")
```

## Excercises

1. Go to the header and replace "html_document" by "word_document". Repeat it with "pdf_document" and "beamer_presentation".




## **References**


